\section{Conclusion}

This paper has tried to establish how reinforcement learning can be used to solve dynamic models. I show that using these solution methods allow for solving models otherwise computationally infeasible. I argue that when using such methods, there is no guarantee of finding the optimal policy, and there exists a real risk of ending up in local maxima. Furthermore have I presented an economic model of exogenous fertility and endogenous female labour supply, that can give a surprisingly good fit to data, and show comparable long term penalties for female participation rates, earnings, wage rates and hours worked to contemporary findings by \textcite{kleven_children_2019}, when a household gets a child. 

The first part of the paper, I draw on the literature of female labour supply and fertility to formulate a simple dynamic model of female labour supply and fertility, tracking households over the life cycle, where women can supply a discreet number of hours to the labour force. I use aggregate data for Statistics Denmark to calibrate the parameters of the income process. For this task I assume that the households follows a deterministic strategy with regards to labour supply. I find, the model seem to approximate the income paths of both men and women very well. Next, I present the reader for reinforcement learning and deep learning allowing the reader to have an understanding of the algorithms used for solving the models presented in this paper.  I go on to present three different solution methods: Value function Iteration using deep neural networks for value function approximation, Deep Q-learning and Double Deep Q-Learning. I find that these three solution methods have comparable performance, but the model does not seem to fit the data well! Next i formulate an extension of the inadequate model, and use Double Deep Q-learning as solution method. I estimate the extra parameters using method of simulated moments. Simulating from the model using the estimated parameters, I find that both the participation rate and the average number of supplied hours to the labour force is comparable to what is found in data. Next i compare event graphs to those found by \textcite{kleven_children_2019} and find striking similarities, finding that women do experience a real penalty when getting a child.